FictionEro - Determinants of Reality Beliefs

### 2024-06-27 analysis/3_realness.qmd
95% completed analysis

This graph highlights gender differences and similarities in the ratings of realness across different types of images, indicating a consistent tendency to rate images as highly real across both genders, particularity at the upper end of the realness scale. Both genders exhibit a tendency to rate images as more real as the realness rating increases, with a consistent spike at the highest rating of 1.0 across all image types. Males generally show higher counts of high realness ratings compared to females, especially for relevant images.The patterns for irrelevant and non-erotic images are quite similar between genders, with a uniform distribution and a spike at the highest rating.

@@

<!-- 2. Impact of condition (AI vs Photograph) -->
<!--     2.1. Both genders significantly rate AI-generated images as less real than images labeled as photographs across all relevance categories. -->
<!--     2.2. The reduction in realness ratings for AI-generated images is larger for males than for females. -->
<!--     2.3. For non-erotic images, this difference is significant for males but not for females. -->

<!-- 3. **Impact of Relevance** (Relevant vs. Irrelevant and Non-Erotic) -->
<!--     3.1. Males significantly rate irrelevant images as less real compared to relevant images. -->
<!--     3.2. Females also rate irrelevant images as less real than relevant images, but this difference is not significant. -->
<!--     3.3. Both genders rate non-erotic images as more real than relevant images.This difference is significant for females but not for males. -->

<!-- 4. **Interaction terms** -->
<!--     4.1. Males rate relevant AI-generated images as significantly less real compared to relevant photographs.  -->
<!--     4.2. Females rate relevant AI-generated images as less real compared to relevant photographs, but the reduction is smaller than for males -->
<!--     4.3. Males rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs -->
<!--     4.4. Females rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs  -->
<!--     4.5. For non-erotic images, males rate AI-generated images as significantly less real than photographs -->
<!--     Females rate non-erotic AI-generated images as less real than photographs, but the difference is smaller and not significant.  -->

@@

<!-- 1. For both genders, as beliefs about AI visual capacity increase, realness ratings significantly increase compared to the baseline. -->
<!-- 2. For males, increased beliefs about AI visual capacity significantly decrease realness ratings of irrelevant images compared to the baseline. -->
<!-- 3. For females, increased beliefs about AI visual capacity significantly increase realness ratings for irrelevant images and non-erotic images compared to the baseline. -->
<!-- 4. For females, increased beliefs about AI's visual abilities significantly decrease realness ratings, of irrelevant and AI-generated images, compared to the baseline. -->

@@

<!-- 1. For both genders, increased beliefs in the textual abilities of AI significantly increase realness ratings compared to the baseline. -->
<!-- 2. For females, increased beliefs in AI textual abilities significantly decrease realness ratings of irrelevant and AI-generated images compared to the baseline. -->
<!-- 3. For males, this effect occurs when they are presented with non-erotic images labeled as AI-generated compared to the baseline. -->

@@

<!-- 1. For males, increased self-reported beliefs about AI knowledge significantly decrease realness ratings only for non-erotic images compared to the baseline. -->
<!-- 2. For females, increased self-reported beliefs about AI knowledge significantly increase realness ratings only for irrelevant images labeled as AI-generated compared to the baseline. -->

@@

<!-- 1. Positive attitudes about AI significantly increase realness ratings for both genders compared to the baseline. -->
<!-- 2. For males, the positive effect of positive attitudes towards AI significantly decreases for irrelevant and non-erotic images compared to the baseline. -->
<!-- 3. This effect also occurs when males are presented with relevant images that are labelled AI. -->

@@

<!-- 1. Negative attitudes about AI significantly decrease realness ratings for females compared to the baseline. -->
<!-- 2. For females, negative attitudes towards AI increase realness ratings for relevant images labeled as AI-generated compared to the baseline. -->

@@

<!-- 1. Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for non-erotic images.  -->
<!-- 2. Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for relevant images labelled as AI-generated.  -->

<!-- b) Could not discriminate -->
<!-- 1. Males and females self-report an inability to discriminate AI-generated images was associated with significantly increased realness ratings compared to the baseline -->
<!-- 2. For males and females, incapacity to discriminate AI-generated images was associated with a significant increase in realness ratings for relevant images when labelled AI-generated, as compared to baseline.  -->
<!-- 3. males showed increased realness ratings for irrelevant images labeled as AI-generated, whereas females exhibited decreased realness ratings compared to the baseline.  -->
<!-- 4. For non-erotic images, reporting an incapacity to discriminate AI-generated images was associated with a increase in realness ratings only for males.  -->

<!-- c) AI images are less arousing -->
<!-- 1. For both genders, reporting that AI-generated images are less arousing was associated with a significant decrease in realness ratings, as compared to baseline.  -->
<!-- 2. For males, reporting AI-images as less arousing was further associated with a significant decrease in realness ratings for relevant images labelled as AI-generated, a compared to baseline. -->

<!-- d) Believing labels were not correct -->
<!-- 1. Reporting that the labels were not always correct was associated with a significant decrease in realness ratings for males only, as compared to baseline.  -->
<!-- 2. Reporting that the labels were reversed was associated with a significant decrease in realness for non-erotic images for males only, as compared to baseline.  -->
<!-- 3. Reporting that the labels were reversed was associated with a significant decrease in realness ratings for relevant images labelled AI-generated for females only, as compared to baseline.  -->

@@

>>>>

<!-- This graph highlights gender differences and similarities in the ratings of realness across different types of images, indicating a consistent tendency to rate images as highly real across both genders, particularity at the upper end of the realness scale. Both genders exhibit a tendency to rate images as more real as the realness rating increases, with a consistent spike at the highest rating of 1.0 across all image types. Males generally show higher counts of high realness ratings compared to females, especially for relevant images.The patterns for irrelevant and non-erotic images are quite similar between genders, with a uniform distribution and a spike at the highest rating. -->

@@

<!-- 2. Impact of condition (AI vs Photograph) -->

<!--     2.1. Both genders significantly rate AI-generated images as less real than images labeled as photographs across all relevance categories. -->

<!--     2.2. The reduction in realness ratings for AI-generated images is larger for males than for females. -->

<!--     2.3. For non-erotic images, this difference is significant for males but not for females. -->

<!-- 3. **Impact of Relevance** (Relevant vs. Irrelevant and Non-Erotic) -->

<!--     3.1. Males significantly rate irrelevant images as less real compared to relevant images. -->

<!--     3.2. Females also rate irrelevant images as less real than relevant images, but this difference is not significant. -->

<!--     3.3. Both genders rate non-erotic images as more real than relevant images.This difference is significant for females but not for males. -->

<!-- 4. **Interaction terms** -->

<!--     4.1. Males rate relevant AI-generated images as significantly less real compared to relevant photographs.  -->

<!--     4.2. Females rate relevant AI-generated images as less real compared to relevant photographs, but the reduction is smaller than for males -->

<!--     4.3. Males rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs -->

<!--     4.4. Females rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs  -->

<!--     4.5. For non-erotic images, males rate AI-generated images as significantly less real than photographs -->

<!--     Females rate non-erotic AI-generated images as less real than photographs, but the difference is smaller and not significant.  -->

@@

<!-- 1. For both genders, as beliefs about AI visual capacity increase, realness ratings significantly increase compared to the baseline. -->

<!-- 2. For males, increased beliefs about AI visual capacity significantly decrease realness ratings of irrelevant images compared to the baseline. -->

<!-- 3. For females, increased beliefs about AI visual capacity significantly increase realness ratings for irrelevant images and non-erotic images compared to the baseline. -->

<!-- 4. For females, increased beliefs about AI's visual abilities significantly decrease realness ratings, of irrelevant and AI-generated images, compared to the baseline. -->

@@

<!-- 1. For both genders, increased beliefs in the textual abilities of AI significantly increase realness ratings compared to the baseline. -->

<!-- 2. For females, increased beliefs in AI textual abilities significantly decrease realness ratings of irrelevant and AI-generated images compared to the baseline. -->

<!-- 3. For males, this effect occurs when they are presented with non-erotic images labeled as AI-generated compared to the baseline. -->

@@

<!-- 1. For males, increased self-reported beliefs about AI knowledge significantly decrease realness ratings only for non-erotic images compared to the baseline. -->

<!-- 2. For females, increased self-reported beliefs about AI knowledge significantly increase realness ratings only for irrelevant images labeled as AI-generated compared to the baseline. -->

@@

<!-- 1. Positive attitudes about AI significantly increase realness ratings for both genders compared to the baseline. -->

<!-- 2. For males, the positive effect of positive attitudes towards AI significantly decreases for irrelevant and non-erotic images compared to the baseline. -->

<!-- 3. This effect also occurs when males are presented with relevant images that are labelled AI. -->

@@

<!-- 1. Negative attitudes about AI significantly decrease realness ratings for females compared to the baseline. -->

<!-- 2. For females, negative attitudes towards AI increase realness ratings for relevant images labeled as AI-generated compared to the baseline. -->

@@

<!-- 1. Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for non-erotic images.  -->

<!-- 2. Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for relevant images labelled as AI-generated.  -->

<!-- b) Could not discriminate -->

<!-- 1. Males and females self-report an inability to discriminate AI-generated images was associated with significantly increased realness ratings compared to the baseline -->

<!-- 2. For males and females, incapacity to discriminate AI-generated images was associated with a significant increase in realness ratings for relevant images when labelled AI-generated, as compared to baseline.  -->

<!-- 3. males showed increased realness ratings for irrelevant images labeled as AI-generated, whereas females exhibited decreased realness ratings compared to the baseline.  -->

<!-- 4. For non-erotic images, reporting an incapacity to discriminate AI-generated images was associated with a increase in realness ratings only for males.  -->

<!-- c) AI images are less arousing -->

<!-- 1. For both genders, reporting that AI-generated images are less arousing was associated with a significant decrease in realness ratings, as compared to baseline.  -->

<!-- 2. For males, reporting AI-images as less arousing was further associated with a significant decrease in realness ratings for relevant images labelled as AI-generated, a compared to baseline. -->

<!-- d) Believing labels were not correct -->

<!-- 1. Reporting that the labels were not always correct was associated with a significant decrease in realness ratings for males only, as compared to baseline.  -->

<!-- 2. Reporting that the labels were reversed was associated with a significant decrease in realness for non-erotic images for males only, as compared to baseline.  -->

<!-- 3. Reporting that the labels were reversed was associated with a significant decrease in realness ratings for relevant images labelled AI-generated for females only, as compared to baseline.  -->

@@

## Summary

-   Findings indicate a consistent perception across both genders that AI-generated images are perceived as less realistic compared to photographs. Interestingly, both genders rated non-erotic images as more realistic than relevant and irrelevant images.

-   As beliefs in AI's ability to generate realistic images increases, both genders show higher realness scores.

-   Porn usage moderated realness ratings, only for men presented with AI-generated non-erotic images.

-   Males who reported an inability to discriminate AI-generated images perceived both relevant and irrelevant AI-generated images as more real, whereas females who reported this inability showed increased realness ratings only for relevant AI-generated images.
